### 2016-05-03 tikz/settings.tex
presentation walks, pebble simulation

\usetikzlibrary{patterns, arrows, cd, positioning, backgrounds, fit, decorations.pathmorphing, shapes.misc, calc, matrix, decorations.pathreplacing}
\tikzset{%
  node/.style={draw, minimum size=12mm, inner sep=0mm, circle, fill=gray!50},
  edge/.style={thick},
  move/.style={->},
  brace/.style={
    decorate,
    decoration={brace,amplitude=10pt,mirror},
  },
  table nodes/.style={
    rectangle,
    draw=black,
    align=center,
    minimum height=7mm,
    text depth=0.5ex,
    text height=2ex,
    inner xsep=0pt,
    outer sep=0pt
  },
  table/.style={
    matrix of nodes,
    row sep=\pgflinewidth,
    column sep=\pgflinewidth,
    nodes={
      table nodes
    }
  }
}

>>>>

\usetikzlibrary{patterns, arrows, cd, positioning, backgrounds, fit, decorations.pathmorphing, shapes.misc, calc, matrix, decorations.pathreplacing}
\tikzset{%
  node/.style={draw, minimum size=12mm, inner sep=0mm, circle, fill=gray!50},
  edge/.style={thick},
  move/.style={->},
  brace/.style={
    decorate,
    decoration={brace,amplitude=10pt,mirror},
  },
  table nodes/.style={
    rectangle,
    draw=black,
    align=center,
    minimum height=7mm,
    text depth=0.5ex,
    text height=2ex,
    inner xsep=0pt,
    outer sep=0pt,
    inner sep=0pt
  },
  table/.style={
    matrix of nodes,
    row sep=-0.5pt,
    column sep=-0.5pt,
    nodes={
      table nodes
    }
  }
}

### 2016-05-03 tikz/tapesimpebsep.tex
presentation walks, pebble simulation

\begin{tikzpicture}
  \matrix (tape) [table, text width=7mm, name=tape]
    { 1 & 1 & 0 & 0 & 1 & 0 & 0 & 1 & 1 & 0 & 0 & 0 \\};

  \node[above=of tape-1-1.west] (s1) {};
  \node[below=of tape-1-1.west] (s2) {};

  \node[above=of tape-1-3.east] (s3) {};
  \node[below=of tape-1-3.east] (s4) {};

  \node[above=of tape-1-6.east] (s5) {};
  \node[below=of tape-1-6.east] (s6) {};

  \node[above=of tape-1-9.east] (s7) {};
  \node[below=of tape-1-9.east] (s8) {};

  \node[above=of tape-1-12.east] (s9) {};
  \node[below=of tape-1-12.east] (s10) {};

  \uncover<2-2>{\draw[brace] (tape-1-12.north east) -- node[yshift=6mm] {$m = 12$} (tape-1-1.north west);}
  \uncover<3->{\draw[brace] (s9.center) -- node[yshift=6mm] {$m = 12$} (s1.center);}

  \uncover<3->{
    \draw[dashed] (s1) to (s2);
    \draw[dashed] (s3) to (s4);
    \draw[dashed] (s5) to (s6);
    \draw[dashed] (s7) to (s8);
    \draw[dashed] (s9) to (s10);
  }

  \uncover<3-3>{
    \draw[brace] (tape-1-1.south west) -- node[yshift=-6mm] {$m_{1} = 3$} (tape-1-3.south east);

    \draw[brace] (tape-1-4.south west) -- node[yshift=-6mm] {$m_{1} = 3$} (tape-1-6.south east);

    \draw[brace] (tape-1-7.south west) -- node[yshift=-6mm] {$m_{1} = 3$} (tape-1-9.south east);

    \draw[brace] (tape-1-10.south west) -- node[yshift=-6mm] {$m_{1} = 3$} (tape-1-12.south east);
  }
  \uncover<4-4>{
    \draw[brace] (tape-1-1.south west) -- node[yshift=-6mm]  {$p_{0}$} (tape-1-3.south east);

    \draw[brace] (tape-1-4.south west) -- node[yshift=-6mm]  {$p_{1}$} (tape-1-6.south east);

    \draw[brace] (tape-1-7.south west) -- node[yshift=-6mm]  {$p_{2}$} (tape-1-9.south east);

    \draw[brace] (tape-1-10.south west) -- node[yshift=-6mm] {$p_{3}$} (tape-1-12.south east);
  }
\end{tikzpicture}

>>>>

\begin{tikzpicture}
  \matrix (tape) [table, text width=7mm, name=tape]
    { 1 & 1 & 0 & 0 & 1 & 0 & 0 & 1 & 1 & 0 & 0 & 0 \\};
  \draw[brace] (tape-1-1.south west) -- node[yshift=-6mm] {$p_{0}$} (tape-1-3.south east); 
  \draw[brace] (tape-1-4.south west) -- node[yshift=-6mm] {$p_{1}$} (tape-1-6.south east); 
  \draw[brace] (tape-1-7.south west) -- node[yshift=-6mm] {$p_{2}$} (tape-1-9.south east); 
  \draw[brace] (tape-1-10.south west) -- node[yshift=-6mm] {$p_{3}$} (tape-1-12.south east); 
\end{tikzpicture}
